\mytitle

### 2016-06-28 paper.tex
paper.tex - camera-ready version
paper.tex - add hyperref options:linkcolor,pdfmetas

\title{bot.zen @ EmpiriST 2015 - A minimally-deep learning PoS-tagger \\
       (trained for German CMC and Web data)}

@@

    The system combines a small assertion of trending techniques, which
    implement matured methods, from NLP and ML to achieve competitive results
    on PoS tagging of German CMC and Web corpus data; in particular, the system
    uses word embeddings and character-level representations of word beginnings
    and endings in a LSTM RNN architecture.  
    Available labelled data (Tiger v2.2 and EmpiriST) and unlabelled data
    (German Wikipedia) was used for training.

>>>>

\newcommand{\mytitle}{bot.zen @ EmpiriST 2015 - A minimally-deep learning PoS-tagger \\
    (trained for German CMC and Web data)}
\newcommand{\mypdftitle}{\mytitle}
\newcommand{\mypdfsubject}{in Proceedings of the 10th Web as Corpus Workshop
    (WAC-X) and the EmpiriST Shared Task}
\newcommand{\mystitle}{bot.zen - A minimally-deep learning PoS-tagger}
\newcommand{\mykeywords}{PoS tagger, word empbeddings, word2vec, neural
    network, RNN, LSTM, EmpiriST 2015 shared task}
\newcommand{\mypdfkeywords}{\mykeywords}

%%%% hyper & options
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}

\usepackage[final=true, pdfstartview=FitH]{hyperref}
\hypersetup{
    pdftitle={\mypdftitle},
    pdfauthor={egon w. stemle <egon.stemle@eurac.edu>},
    pdfsubject={\mypdfsubject},
    pdfkeywords={\mypdfkeywords},
    setpagesize=true,
    colorlinks=true,
    linkcolor=darkred,
    urlcolor=darkblue,
    citecolor=darkgreen
}

\title{\mytitle}

@@

    The system combines a small assertion of trending techniques, which
    implement matured methods, from NLP and ML to achieve competitive results
    on PoS tagging of German CMC and Web corpus data; in particular, the system
    uses word embeddings and character-level representations of word beginnings
    and endings in a LSTM RNN architecture.  
    Labelled data (Tiger v2.2 and EmpiriST) and unlabelled data (German
    Wikipedia) were used for training.
